Using an iterated block particle filter via \pkg{spatPomp}

### 2024-08-06 ms.Rnw
re-run on greatlakes
recompiled and update references

\title{Using an iterated block particle filter via \pkg{spatPomp}}
\author{Ning Ning and Edward L. Ionides}
\date{\small Compiled \today,  using \proglang{R} \Sexpr{paste0(R.version$major,".",R.version$minor)}, \pkg{spatPomp} \Sexpr{packageVersion('spatPomp')}, and \pkg{pomp} \Sexpr{packageVersion('pomp')}\\
Source code at \url{https://github.com/ionides/ibpf-tutorial}}
\begin{document}
\maketitle

@@

>>>>

\title{Using an iterated block particle filter via \pkg{spatPomp}}
\author{Ning Ning and Edward L. Ionides}
\date{\small This version compiled on \today,  using \proglang{R} \Sexpr{paste0(R.version$major,".",R.version$minor)}, \pkg{spatPomp} \Sexpr{packageVersion('spatPomp')}, and \pkg{pomp} \Sexpr{packageVersion('pomp')}\\
Source code at \url{https://github.com/ionides/ibpf-tutorial}}
\begin{document}
\maketitle

@@

\section{Discussion}

Further examples of \code{ibpf} being used for data analysis are provided by \citet{li24} and \citet{wheeler24}.
\citet{li24} studied the spread of COVID-19 in China at the start of the pandemic.
Their models are available in the \code{metapoppkg} R package (\url{https://doi.org/10.5281/zenodo.10149233}) and the article source code is available at \url{https://doi.org/10.5281/zenodo.10149258}.
\citet{wheeler24} studied a cholera epidemic in Haiti.
Their models are available in the \code{haitipkg} R package (\url{https://doi.org/10.5281/zenodo.7557099}) and the article source code is available at \url{https://doi.org/10.5281/zenodo.10783080}.
